\clearpage\newpage
\section{Automated tests}

The project runs automatic unitary tests at every commit. The tests run in the front-end's domain layer with the Jest library.

I created this test subject that has several evaluations, each one with particularities, to run tests on them using different combinations of grades.

\begin{minted}[
    baselinestretch=0.65,
]{typescript}
{
  shortName: "TEST",
  fullName: "Testing subject",
  course: "Q2 2019-2020",
  uni: "UPC",
  faculty: "FIB",
  color: 1,
  evaluations: [
    {
      name: "E1 All same weights",
      exams: [
        { name: "A1", weight: 0.25, type: "A" },
        { name: "A2", weight: 0.25, type: "A" },
        { name: "A3", weight: 0.25, type: "A" },
        { name: "A4", weight: 0.25, type: "A" }
      ]
    }, {
      name: "E2 All different weights",
      exams: [
        { name: "B1", weight: 0.2, type: "B" },
        { name: "B2", weight: 0.3, type: "B" },
        { name: "B3", weight: 0.5, type: "B" },
      ]
    }, {
      name: "E3 Some same and different weights",
      exams: [
        { name: "C1", weight: 0.1, type: "C" },
        { name: "C2", weight: 0.1, type: "C" },
        { name: "C3", weight: 0.8, type: "C" }
      ]
    }, {
      name: "E4 Repeated exam names",
      exams: [
        { name: "C1", weight: 0.5, type: "C" },
        { name: "C2", weight: 0.5, type: "C" }
      ]
    }, {
      name: "E5 Weight's sum greater than 1",
      exams: [
        { name: "D1", weight: 1, type: "D" },
        { name: "D2", weight: 1, type: "D" }
      ]
    }
  ],
  creationDate: "April 1, 2020 at 7:12:44 PM UTC+1",
  creator: "Maurici Abad Gutierrez",
  creatorId: "4wUPZqVqt1Y9K6CAWLBNlZwe3b12"
}
\end{minted}

\clearpage\newpage\noindent
Below are the unitary tests (UT) grouped by what they test.

\nextAutoTest{The order doesn't matter}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Sets all the grades to 10 in all possible orders. 
    \item \textbf{Result}: \texttt{necessary}=0 and \texttt{final}=$(10*\text{sum of weights})$
    \item \textbf{Variations}: All evaluations $\times$ All exam orders.
\end{itemize}
\vfill
\nextAutoTest{Empty grades}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Leave all exams undone.
    \item \textbf{Result}: \texttt{necessary}=$\frac{5}{\text{sum of weights}}$ and \texttt{final}=0
    \item \textbf{Variations}: All evaluations
\end{itemize}
\vfill
\nextAutoTest{Normal grades, not all filled}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Fill the evaluations with some grades from 0 to 10 with decimals, but leaving at least one empty exam. 
    \item \textbf{Result}: \texttt{necessary} and \texttt{final} depend on the combination.
    \item \textbf{Variations}: All evaluations $\times$ 5 grades combinations
\end{itemize}
\vfill
\nextAutoTest{Normal grades, all filled}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Fill the evaluations with some grades from 0 to 10 with decimals, but filling all the exams. 
    \item \textbf{Result}: \texttt{necessary} and \texttt{final} depend on the combination.
    \item \textbf{Variations}: All evaluations $\times$ 5 grades combinations
\end{itemize}
\vfill
\nextAutoTest{Necessary is never negative}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Set some grades that make \texttt{final} $\geq$ 5\\
        In E4, set C1 to 10 \\
        In E5, set D1 to 10 \\
        In E2, set B2 and B3 to 10
    \item \textbf{Result}: \\
        \texttt{necessary}=0 and \texttt{final}=5 \\
        \texttt{necessary}=0 and \texttt{final}=10 \\
        \texttt{necessary}=0 and \texttt{final}=7
    \item \textbf{Variations}: 3 cases.
\end{itemize}
\vfill
\nextAutoTest{Necessary can be greater than 10}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Set some grades that make \texttt{necessary} $\geq$ 10\\
        In E1, set A1, A2 and A3 to 0 \\
        In E2, set B2 and B3 to 0 \\
        In E3, set C2 and C3 to 0 \\
        In E3, set C2 and C3 to 4.33 
    \item \textbf{Result}: \\
        \texttt{necessary}=20 and \texttt{final}=0 \\
        \texttt{necessary}=25 and \texttt{final}=0 \\
        \texttt{necessary}=100 and \texttt{final}=0 \\
        \texttt{necessary}=11 and \texttt{final}=0
    \item \textbf{Variations}: 4 cases.
\end{itemize}
\vfill
\nextAutoTest{Negative grades}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Set some exams to -10. \\
        In E1, set A1 to -10 \\
        In E1, set A1 and A2 to -10 \\
        In E2, set B2 and B3 to -10 \\
        In E5, set D1 to -10 \\
        In E2, set B1 to -10
    \item \textbf{Result}: \\
        \texttt{necessary}=10 and \texttt{final}=-2.5 \\
        \texttt{necessary}=20 and \texttt{final}=-5 \\
        \texttt{necessary}=65 and \texttt{final}=-8 \\
        \texttt{necessary}=15 and \texttt{final}=-10 \\
        \texttt{necessary}=8.75 and \texttt{final}=-10  
    \item \textbf{Variations}: 5 cases.
\end{itemize}
\vfill
\nextAutoTest{Grades greater than 10}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: Set some exams to -10. \\
        In E2, set B1 to 11 \\
        In E4, set C1 to 11 \\
        In E4, set C1 to 100 
    \item \textbf{Result}: \\
        \texttt{necessary}=3.5 and \texttt{final}=2.2 \\
        \texttt{necessary}=0 and \texttt{final}=5.5 \\
        \texttt{necessary}=0 and \texttt{final}=50 
    \item \textbf{Variations}: 3 cases.
\end{itemize}
\vfill
\nextAutoTest{Grades are shared}
\begin{itemize}[noitemsep]
    \item \textbf{Description}: In E3 set C1 and C2 to 10. And then change the evaluation to E4.
    \item \textbf{Result}: \\
        In E3: \texttt{necessary}=3.75 and \texttt{final}=2 \\
        In E4: \texttt{necessary}=0 and \texttt{final}=10
    \item \textbf{Variations}: Fill E3 and then E4 + Fill E4 and then E3.
\end{itemize}
\vfill

% \nextAutoTest{}
% \begin{itemize}[noitemsep]
%     \item \textbf{Description}: 
%     \item \textbf{Result}: \texttt{necessary}= and \texttt{final}=
%     \item \textbf{Variations}: All evaluations $\times$ 
% \end{itemize}


% \begin{autoTestTable}{
%     Every 
% }
% 1. & A1=10 & necessary=3.33 and final=2.5 \\
% 1. & Clear all & necessary=5 and final=0 \\
% 1. & A2=10 & necessary=3.33 and final=2.5 \\
% 1. & Clear all & necessary=5 and final=0 \\
% 1. & A3=10 & necessary=3.33 and final=2.5 \\
% 1. & Clear all & necessary=5 and final=0 \\
% 1. & A4=10 & necessary=3.33 and final=2.5 \\
% \end{autoTestTable}